Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-16 analysis/paper/paper.Rmd
Wordsmithing and clean up statistical analysis

All authors agreed on the inter-rater article evaluations for the data availability, '0', not available, but one of the authors rated one article as `NA` or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.

## Code and Data Sharing Classification Scores

@@

When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A).

When predicting the availability of data availability as compared with *Phytopathology* two journals were not likely to share data, with the others being unable to detect any effect.
Publications in three journals, *Crop Protection*, *Plant Disease* and *Revista Mexicana de Fitopatología*, can be considered clearly less likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title.
The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).

There was no effect detected for year when predicting the availability of computational methods (code) availability.
However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
There was no detectable pattern in increasing or decreasing availability of data in the years examined.

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.

No journals surveyed were completely closed, all offered at least an option for open access articles but `r rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()` (`r round(rrpp %>% distinct(abbreviation, open) %>% filter(open == TRUE) %>% nrow()/nrow(rrpp), 2)`%) were completely open.

>>>>

All authors agreed on the five inter-rater article evaluations for the data availability, '0', not available for a inter-rater score of 100%.
However, one of the authors rated one article as 'NA' or not having any computational methods used rather than '0' as with the other four authors, giving the inter-rater percent agreement a score of 100% with the 'NA' value dropped from the code availability.

## Code and Data Sharing Findings

@@
